%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}
%------------------------------------------------

\cventry
{Advisor \& Investor} % Job title
{Under Pressure Testing} % Organization
{Kirkland, WA} % Location
{Jun. 2015 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
	\begin{cvitems}
		\item {Advising on business system design, business process and market strategy for professional services company in the construction field.}
	\end{cvitems}
}


%------------------------------------------------

\cventry
{Operations Manager} % Job title
{Hennessey Wellness} % Organization
{San Francisco, CA} % Location
{Oct. 2015 - Apr. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Responsible for internal, partner and customer facing company operations. Built and managed customer and partner facing services team. Developed and maintained HIPAA compliant protocols. Ensured team adherance to secure protocols.}
\item {Developed and implemented partner vendor due diligence process. Recruited strategic partners to Hennessey Wellness platform to serve HW clients. Reviewed and edited legal agreements for business intent prior to external counsel review and approval.}
%\item {Developed KPIs and related reporting to manage company and partner performance.}
\item {Worked closely with product and executive leadership teams. Provided cost and capacity analysis with recommendations to executive leadership when developing new programs.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Product Manager, Business Platform} % Job title
{} % Organization
{} % Location
{Jun. 2014 - Sep. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Charged with requirements definition, design, implementation and execution of the Hennessey Wellness internal and partner facing operations systems. Supported custom client facing platform design and implementation.}
\item {Created automated and dynamic checklist generation functionality to ensure consistent adherence to complex customer service protocols. Designed and managed implementation of HIPAA compliant messaging client communication system.}
\item {Designed and implemented proprietary HIPAA compliant system to capture sensitive client health information. System automatically populated the captured information into external health provider forms on-demand. Resulted in reduced hassle and meaningful time savings for clients when seeing a new health provider.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Business Operations Manager} % Job title
{b-efficient, Inc.} % Organization
{Corte Madera, CA} % Location
{Jan. 2014 - May. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Manager responsible for central reporting and analytical support to all business units. Owner of core business infrastructure necessary for company operations. Provided documentation and training for all company personnel in effective use of technology at company.}
\item {Launched and managed Office365, Salesforce.com with Partner Community, RingCentral(integrated with Salesforce.com), Conga Composer and MailChimp business systems. Setup physical IP phones in office to work with RingCentral VOIP service.}
\item {Created system for automated sales proposal generation. Enabled sales reps to build and send proposals on their own, expediting the sales process and improving quality control of solutions presented to potential customers. Incorporated automated approval process.}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{Business Operations Manager} % Job title
{Clean Power Finance (now Spruce Finance)} % Organization
{San Francisco, CA} % Location
{Jan. 2012 - Jan. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
%\item {Responsible for central reporting and analytical support to executive management, sales, marketing, customer support and operations teams.}
\item {Owner of central reporting and analytical support functions at company. Managed roadmap of enhancements to central infrastructure and reporting supporting key company objectives. Routinely interface with key stakeholders in executive management, sales, operations, marketing and customer support teams to prioritize roadmap, deliver insights and provide data driven business recommendations. Delivered company ``Heartbeat'' dashboard used daily by executive team to monitor overall health of the company.}
\item {Built central engine for underwriting team to efficiently process all solar lease and ppa projects for the company. Automated routing of projects at various stages to appropriate team members. Built sophisticated dashboards and reports with Tableau Server, Microsoft SQL Server and Salesforce.com to assess individual and team performance in real time. Helped eliminate large backlog and significantly improved processing times for project underwriting. Improved company cashflow and increased deal flow capacity.}
\item {Created and led cross-functional analyst team. Mentored junior analysts and increased each department’s ability to analyze local data and speed up decision making. Increased my team’s bandwidth to focus on larger and more complex corporate initiatives.}
\item {Worked with customer support team to transition from Salesforce.com to Zendesk. Built a JavaScript plugin to connect Zendesk to CPF platform for streamlined customer support. Transitioned marketing team to Marketo for robust campaign automation and reporting.}
%\item {Implemented Marketo for marketing team. Worked to define customer journey. Helped setup HTML communication templates.}
%\item {Responsible for providing accurate reporting to support key company objectives and identify opportunities for improvement within business processes. Facilitated the implementation, use and enhancement of automation tools to streamline sales, marketing and operations workflows. Increased alignment across all departments via internal infrastructure and process development.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Sales Operations Analyst} % Job title
{} % Organization
{} % Location
{Jan. 2011 - Dec. 2011} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Provided reporting and analytical support to the sales and executive management team. Built central sales dashboard used by leadership to measure performance of sales organization.}
\item {Migrated company from open source CRM to Salesforce.com without loss of data or interruption of sales activities. Worked with engineering team to integrate proprietary CPF platform with Salesforce.com. Improved visibility for individual CPF sales reps and management into channel sales results.}
%\item {Automated many repetitive sales tasks inside Salesforce.com.}
\item {Maintained accurate reporting tools to support sales objectives. Identified opportunities for improvement with sales operations processes. Facilitated the implementation, use and enhancement of automation tools with the sales process to maximize sales productivity.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Inside Sales Representative} % Job title
{} % Organization
{} % Location
{Feb. 2010 - Dec. 2010} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Articulated CPF’s vision and products to the marketplace. Increased CPF revenue through sales of CPF Tools subscriptions, Leads, 3D Roof Analysis and Automated Rebate Forms. Prospected for new business while supporting existing accounts through online trainings, phone and email outreach. Accomplished consistent revenue growth every quarter  while posting the single largest ISR sale in 2010.} %(Q1-Q2 +293\%|Q2-Q3 +48\%|Q3-Q4 +4\%)
%\item {Revamped weekly sales webinar presentation to shorten sales cycle.} 
\item {Set new paradigm for transparency and reporting of sales efforts, allowing ISRs and management to understand progress of sales activities towards revenue goals. Provided key data to enable channel sales team to articulate CPF advantage in the marketplace to manufacturers and distributors of Solar PV. Tracked and reported results of sales campaigns.}
\item {Led team for internal company initiative to overhaul the business process and IT systems to bring increased productivity by the inside sales team. Presented findings to executive team.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Market Analyst} % Job title
{} % Organization
{} % Location
{Feb. 2009 - Jan. 2010} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
	\item {Conducted market research for CPF Tools, the company’s proprietary solar quote-generating software.}
	\item {Establish relations with utility companies and commissions. Built database of application procedures for solar incentive programs across the United States. Produced technical documentation outlining application processes. Educated sales and product teams to support CPF Automated Rebate Forms sales.}
\end{cvitems}
}
%------------------------------------------------

\end{cventries}