%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}
%------------------------------------------------

\cventry
{Business Development and Data Analytics Lead} % Job title
{643 Consulting} % Organization
{Kirkland, WA} % Location
{Nov. 2018 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Responsible for generating new business opportunities, maintaining client relationships, and providing data analytics services for 643 Consulting. 643 Consulting specializes in custom software development and business intelligence services for enterprise clients.}
\end{cvitems}
}
{
\begin{cvitemsnb}
\item {Key data technologies, tools and business systems supported: MS PowerBI, MS Excel \& VBA, Microsoft Sharepoint, Tableau/TableauOnline, PeriscopeData, Salesforce.com, Matillion ETL, Amazon Redshift, MS SQL Server and SSIS, MySQL}
\end{cvitemsnb}
}
%------------------------------------------------
	
\cventry
{Senior Manager Sales Analytics} % Job title
{Mosaic} % Organization
{Oakland, CA} % Location
{Jul. 2016 - Oct. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Provided strategic analytical support to key partners, sales and executive teams. Used data to shape product design, help win accounts, monitor health of existing partners, and increase customer conversion. Coordinated sales forecasting, planning and budgeting processes.}
\end{cvitems}
}
\begin{cvitemsnb}
%\item {Results:}
\item {Results: Designed 3rd generation loan pricing menu. Achieved target portfolio weighted average coupon and maintained \$1B annualized loan volume. Built data warehouse (Amazon Redshift) and ETL processes to centralize CRM and company SaaS platform data. Built interactive self-serve reporting (Tableau, PeriscopeData) and simplified SQL queries. Standardized partner facing reporting. Trained sales team to understand trends and communicate findings to partners. Created data driven forecasts and facilitated sales team forecasting process.}
\end{cvitemsnb}
	
%------------------------------------------------

\cventry
{Operations Manager} % Job title
{Hennessey Wellness} % Organization
{San Francisco, CA} % Location
{Oct. 2015 - Apr. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Responsible for internal, partner and customer facing company operations. Built and managed customer- and partner-facing services team. Developed and maintained HIPAA compliant protocols. Ensured team adherence to secure protocols via auditing and training.}
\end{cvitems}
}
\begin{cvitemsnb}
%\item {Results:}
\item {Results: Created capacity and growth models to show viability of new programs. Built reports and dashboards to monitor health of business. Developed and implemented standard due diligence process for partners. Recruited strategic partners to join HW platform.}
\end{cvitemsnb}

%------------------------------------------------    

\cventry
{Product Manager, Business Platform} % Job title
{} % Organization
{} % Location
{Jun. 2014 - Sep. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Charged with requirements definition, design, implementation and execution of the Hennessey Wellness internal and partner-facing operations systems. Supported custom client-facing platform design and implementation.}
\end{cvitems}
}
\begin{cvitemsnb}
%\item {Results:}
\item {Results: Created automated dynamic checklist system for complex customer service protocols. Designed and managed HIPAA-compliant client messaging system. Built HIPAA-compliant client health data intake system to populate external health provider forms on-demand.}
\end{cvitemsnb}


%------------------------------------------------

\cventry
{Business Operations Manager} % Job title
{b-efficient, Inc.} % Organization
{Corte Madera, CA} % Location
{Jan. 2014 - May. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Manager responsible for central reporting and analytical support to all business units. Owner of core business infrastructure necessary for company operations. Provided documentation and training for all company personnel in effective use of technology at company.}
\end{cvitems}
%\item {Launched and managed Office365, Salesforce.com with Partner Community, RingCentral(integrated with Salesforce.com), Conga Composer and MailChimp business systems. Setup physical IP phones in office to work with RingCentral VOIP service.}
%\item {Created system for automated sales proposal generation. Enabled sales reps to build and send proposals on their own, expediting the sales process and improving quality control of solutions presented to potential customers. Incorporated automated approval process.}
}
\begin{cvitemsnb}
%\item {Results:}
\item {Results: Built sales compensation plan for CEO. Launched and managed essential business systems (Salesforce.com, RingCentral, Conga, MailChimp). Automated sales proposal generation empowering reps, shortening sales cycle and implementing robust pricing controls.}
\end{cvitemsnb}

%------------------------------------------------

\cventry
{Business Operations Manager} % Job title
{Clean Power Finance (now Spruce Finance)} % Organization
{San Francisco, CA} % Location
{Jan. 2012 - Jan. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Owner of central analytical support functions and infrastructure at company. Routinely interfaced with key stakeholders in executive management, sales, operations, marketing and customer support teams to prioritize infrastructure road map, deliver insights, and provide data driven business recommendations. Supported customer-facing teams with technology to improve and simplify business processes.}
\end{cvitems}
}
\begin{cvitemsnb}
%\item {Results:}
\item {Results: Improved company cash flow and scaled underwriting capacity by creating central engine used by operations team to efficiently process all solar leases and PPAs. Created real time reporting of individual and team underwriting performance. Delivered daily company ``Heartbeat'' KPI report (Tableau) to executive team. Created and led cross-functional business analyst team. Mentored junior analysts.}
\end{cvitemsnb}

%------------------------------------------------

\cventry
{Sales Operations Analyst} % Job title
{} % Organization
{} % Location
{Jan. 2011 - Dec. 2011} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Maintained accurate reporting tools to support sales objectives. Provided reporting and analytical support to the sales and executive management team. Identified opportunities for improvement with sales operations processes. Facilitated the implementation, use, and enhancement of automation tools with the sales process to maximize sales productivity.}
\end{cvitems}
}
\begin{cvitemsnb}
%\item {Results:}
\item {Results: Migrated company from open source CRM to Salesforce.com without loss of data or interruption of sales activities. Integrated CPF platform with Salesforce.com. Built central sales dashboard (Salesforce.com) used by leadership to measure performance of sales team.}
\end{cvitemsnb}
%------------------------------------------------

\cventry
{Inside Sales Representative} % Job title
{} % Organization
{} % Location
{Feb. 2010 - Dec. 2010} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Articulated CPF’s vision and products to the marketplace. Increased CPF revenue through sales of CPF Tools subscriptions, Leads, and 3D Roof Analysis. Prospected for new business while supporting existing accounts through online trainings, phone and email outreach.} %(Q1-Q2 +293\%|Q2-Q3 +48\%|Q3-Q4 +4\%)
\end{cvitems}
}
\begin{cvitemsnb}
%\item {Results:}
\item {Results: Accomplished consistent revenue growth every quarter. Had largest ISR sale of 2010. Set new paradigm for transparency of sales efforts. Led internal team to overhaul processes and IT systems to increase sales productivity and presented findings to executive team.}
\end{cvitemsnb}	

%------------------------------------------------

\cventry
{Market Analyst} % Job title
{} % Organization
{} % Location
{Feb. 2009 - Jan. 2010} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Conducted market research for CPF Tools, the company’s proprietary solar quote-generating software. Established relations with utility companies and commissions. Educated sales and product teams to support CPF Automated Rebate Forms sales.}
\end{cvitems}
}
\begin{cvitemsnb}
%\item {Results:}
\item {Results: Built database and supporting technical documentation of application procedures for solar incentive programs across the US.}
\end{cvitemsnb}	

%------------------------------------------------

\end{cventries}