%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}
%------------------------------------------------

\cventry
{Director of Business Development and Operations} % Job title
{Govurn} % Organization
{Bellevue, WA} % Location
{Nov. 2018 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Reporting to the CEO. Tasked with supporting capital raising activities, building early stage customer pipeline and shaping product development process.}
\end{cvitems}
}
%------------------------------------------------

\cventry
{Owner and Advisor} % Job title
{Under Pressure Testing} % Organization
{Kirkland, WA} % Location
{Jun. 2015 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
	\begin{cvitems}
		\item {Advising on business system design, business process development and market strategy for professional services company.}
	\end{cvitems}
}
\begin{cvitemsnb}
	%\item {Results:}
	\item {Results: Oversaw CRM design and implementation. Implemented automated proposal generation system. Setup sales reports and dashboard. Put in place revenue forecasting methodology.}
\end{cvitemsnb}

%------------------------------------------------
	
\cventry
{Senior Manager Sales Analytics} % Job title
{Mosaic} % Organization
{Oakland, CA} % Location
{Jul. 2016 - Oct. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Responsible for analytical support to sales organization. Used data to help win accounts and increase customer conversion. Provided sales engineering support for strategic partnerships. Coordinated sales forecasting, planning and budgeting processes used within the sales organization. Managed and interpret competitive market intelligence.}
\end{cvitems}
}
\begin{cvitemsnb}
%\item {Results:}
\item {Results: Designed pricing menu for loan products to increase weighted average coupon while maintaining wallet share of partner network. Standardized process for account managers to understand trends and communicate findings to partners via partner facing reports. Created centralized data warehouse and built ETL processes to bring data from CRM and proprietary SaaS platform together to drive self service reporting and make more complex queries more efficient. Created series of self service dashboards and reporting resources to handle standard KPIs and common inquiries from Sales and Executive Leadership teams. Created sales forecasts from pipeline data as well as facilitated forecasting process for entire sales team. Handled complex queries for sales team and company as a whole. Trained other analyst resources at the company.}
\end{cvitemsnb}
	
%------------------------------------------------

\cventry
{Operations Manager} % Job title
{Hennessey Wellness} % Organization
{San Francisco, CA} % Location
{Oct. 2015 - Apr. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Responsible for internal, partner and customer facing company operations. Built and managed customer and partner facing services team. Developed and maintained HIPAA compliant protocols. Ensured team adherence to secure protocols via auditing and training.}
\end{cvitems}
}
\begin{cvitemsnb}
%\item {Results:}
\item {Results: Created capacity and growth models to show viability of new programs. Built reports and dashboards to monitor health of business. Developed and implemented standard due diligence process. Recruited strategic partners to join HW platform.}
\end{cvitemsnb}

%------------------------------------------------    

\cventry
{Product Manager, Business Platform} % Job title
{} % Organization
{} % Location
{Jun. 2014 - Sep. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Charged with requirements definition, design, implementation and execution of the Hennessey Wellness internal and partner facing operations systems. Supported custom client facing platform design and implementation.}
\end{cvitems}
}
\begin{cvitemsnb}
%\item {Results:}
\item {Results: Created automated dynamic checklist system for complex customer service protocols. Designed and managed implementation of HIPAA compliant client messaging system. Designed and implemented cloud based HIPAA compliant client health data capture system and automatically populated external health provider forms on-demand.}
\end{cvitemsnb}


%------------------------------------------------

\cventry
{Business Operations Manager} % Job title
{b-efficient, Inc.} % Organization
{Corte Madera, CA} % Location
{Jan. 2014 - May. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Manager responsible for central reporting and analytical support to all business units. Owner of core business infrastructure necessary for company operations. Provided documentation and training for all company personnel in effective use of technology at company.}
\end{cvitems}
%\item {Launched and managed Office365, Salesforce.com with Partner Community, RingCentral(integrated with Salesforce.com), Conga Composer and MailChimp business systems. Setup physical IP phones in office to work with RingCentral VOIP service.}
%\item {Created system for automated sales proposal generation. Enabled sales reps to build and send proposals on their own, expediting the sales process and improving quality control of solutions presented to potential customers. Incorporated automated approval process.}
}
\begin{cvitemsnb}
%\item {Results:}
\item {Results: Developed and modeled sales compensation plan for CEO. Launched and managed essential business systems including Salesforce.com, RingCentral, Conga Composer and MailChimp. Automated sales proposal generation empowering reps, shortening sales cycle and improving management's control over pricing to all customers.}
\end{cvitemsnb}

%------------------------------------------------

\cventry
{Business Operations Manager} % Job title
{Clean Power Finance (now Spruce Finance)} % Organization
{San Francisco, CA} % Location
{Jan. 2012 - Jan. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Owner of central reporting and analytical support functions at company. Managed road map of enhancements to central reporting infrastructure supporting key company objectives. Routinely interface with key stakeholders in executive management, sales, operations, marketing and customer support teams to prioritize road map, deliver insights and provide data driven business recommendations. Supported customer facing teams with technology to improve and simplify process.}
\end{cvitems}
}
\begin{cvitemsnb}
%\item {Results:}
\item {Results: Delivered daily company ``Heartbeat'' report to executive team with interactive KPIs. Created reporting to assess individual and team performance of underwriting in real time. Built central engine used by underwriting team to process all solar leases and ppa's processed at the company. Improved company cash flow and increased processing capacity without need for additional headcount. Created and led cross-functional business analyst team and mentored junior analysts.}
\end{cvitemsnb}

%------------------------------------------------

\cventry
{Sales Operations Analyst} % Job title
{} % Organization
{} % Location
{Jan. 2011 - Dec. 2011} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Maintained accurate reporting tools to support sales objectives. Provided reporting and analytical support to the sales and executive management team. Identified opportunities for improvement with sales operations processes. Facilitated the implementation, use and enhancement of automation tools with the sales process to maximize sales productivity.}
\end{cvitems}
}
\begin{cvitemsnb}
%\item {Results:}
\item {Results: Migrated company from open source CRM to Salesforce.com without loss of data or interruption of sales activities. Integrated CPF platform with Salesforce.com. Built central sales dashboard used by leadership to measure performance of sales organization.}
\end{cvitemsnb}
%------------------------------------------------

\cventry
{Inside Sales Representative} % Job title
{} % Organization
{} % Location
{Feb. 2010 - Dec. 2010} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Articulated CPF’s vision and products to the marketplace. Increased CPF revenue through sales of CPF Tools subscriptions, Leads, 3D Roof Analysis and Automated Rebate Forms. Prospected for new business while supporting existing accounts through online trainings, phone and email outreach.} %(Q1-Q2 +293\%|Q2-Q3 +48\%|Q3-Q4 +4\%)
\end{cvitems}
}
\begin{cvitemsnb}
%\item {Results:}
\item {Results: Accomplished consistent revenue growth every quarter. Posted largest ISR sale in 2010. Set new paradigm for transparency and reporting of sales efforts. Led internal team to overhaul business process and IT systems to increase sales productivity and presented findings to executive team.}
\end{cvitemsnb}	

%------------------------------------------------

\cventry
{Market Analyst} % Job title
{} % Organization
{} % Location
{Feb. 2009 - Jan. 2010} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Conducted market research for CPF Tools, the company’s proprietary solar quote-generating software. Establish relations with utility companies and commissions. Educated sales and product teams to support CPF Automated Rebate Forms sales.}
\end{cvitems}
}
\begin{cvitemsnb}
%\item {Results:}
\item {Results: Built database of application procedures for solar incentive programs across the United States. Produced technical documentation outlining application processes.}
\end{cvitemsnb}	

%------------------------------------------------

\end{cventries}